Numerical experiments - market ecology

### 2021-05-04 experiments.tex

There are many many things we can also study:
\begin{itemize}
    \item Influence of strategy space with H
    \item Time horizon of EMA fitness profit
    \item Market parameters: dividend growth rate, volatility, interest rate
    \item Alternative values for agent leverage, aggressiveness of response 
\end{itemize}

>>>>

There are many many things we can also study just with trend followers:
\begin{itemize}
    \item Influence of strategy space with H
    \item Time horizon of EMA fitness profit
    \item Market parameters: dividend growth rate, volatility, interest rate, autocorrelation
    \item Alternative values for agent leverage, aggressiveness of response 
    \item Population size
    \item Tournament size
    \item Reinvestment rate
\end{itemize}

The key area of progress will be to add multiple strategy types, this may require a lot of work on the structure. 3 separate GAs with fixed population sizes? dynamic population sizes?
